\renewcommand{\bibname}{TÀI LIỆU THAM KHẢO}
\addcontentsline{toc}{chapter}{TÀI LIỆU THAM KHẢO}
\begin{thebibliography}{99}

\bibitem{lewis2020rag}
Patrick Lewis et al. \textit{Retrieval-Augmented Generation for Knowledge-Intensive NLP Tasks}. Advances in Neural Information Processing Systems, 2020.

\bibitem{robertson2009bm25}
Stephen Robertson and Hugo Zaragoza. \textit{The Probabilistic Relevance Framework: BM25 and Beyond}. Foundations and Trends in Information Retrieval, 2009.

\bibitem{vaswani2017attention}
Ashish Vaswani et al. \textit{Attention Is All You Need}. Advances in Neural Information Processing Systems, 2017.

\bibitem{devlin2019bert}
Jacob Devlin, Ming-Wei Chang, Kenton Lee, and Kristina Toutanova. \textit{BERT: Pre-training of Deep Bidirectional Transformers for Language Understanding}. NAACL-HLT, 2019.

\bibitem{liu2019roberta}
Yinhan Liu et al. \textit{RoBERTa: A Robustly Optimized BERT Pretraining Approach}. arXiv:1907.11692, 2019.

\bibitem{phobert2020}
Dat Quoc Nguyen and Anh Tuan Nguyen. \textit{PhoBERT: Pre-trained language models for Vietnamese}. Findings of EMNLP, 2020.

\bibitem{biobert2020}
Jinhyuk Lee et al. \textit{BioBERT: a pre-trained biomedical language representation model for biomedical text mining}. Bioinformatics, 36(4):1234--1240, 2020.

\bibitem{clinicalbert2019}
Kexin Huang, Jaan Altosaar, and Rajesh Ranganath. \textit{ClinicalBERT: Modeling Clinical Notes and Predicting Hospital Readmission}. arXiv:1904.05342, 2019.

\bibitem{medpalm2023}
Karan Singhal et al. \textit{Large language models encode clinical knowledge}. Nature, 620:172--180, 2023.

\bibitem{chromadb}
ChromaDB Documentation. \textit{Chroma: the open-source embedding database}. Truy cập cho mục đích triển khai vector retrieval.

\bibitem{bge}
BAAI. \textit{BGE Embedding Models}. Tài liệu và model card của dòng embedding BGE.

\bibitem{dpr2020}
Vladimir Karpukhin et al. \textit{Dense Passage Retrieval for Open-Domain Question Answering}. EMNLP, 2020.

\bibitem{colbert2020}
Omar Khattab and Matei Zaharia. \textit{ColBERT: Efficient and Effective Passage Search via Contextualized Late Interaction over BERT}. SIGIR, 2020.

\bibitem{bert_rerank2019}
Rodrigo Nogueira and Kyunghyun Cho. \textit{Passage Re-ranking with BERT}. arXiv:1901.04085, 2019.

\bibitem{ragas2024}
Shahul Es, Jithin James, Luis Espinosa-Anke, and Steven Schockaert. \textit{RAGAs: Automated Evaluation of Retrieval Augmented Generation}. EACL System Demonstrations, 2024.

\bibitem{ddinter}
DDInter. \textit{Drug-Drug Interaction Database}. Nguồn dữ liệu quan hệ tương tác thuốc--thuốc.

\bibitem{dav}
Cục Quản lý Dược Việt Nam. \textit{Dữ liệu đăng ký thuốc, cảnh báo và thu hồi thuốc}. Sử dụng làm nguồn đối soát trong corpus đồ án.

\bibitem{dav_congbothuoc}
Cục Quản lý Dược Việt Nam. \textit{Cổng công bố thuốc, nguyên liệu làm thuốc tại Việt Nam}. \url{https://dichvucong.dav.gov.vn/congbothuoc/index}. Truy cập ngày 24/06/2026.

\bibitem{dailymed}
National Library of Medicine. \textit{DailyMed: Drug Label Information}. \url{https://dailymed.nlm.nih.gov/}. Truy cập ngày 24/06/2026.

\bibitem{dailymed_api}
National Library of Medicine. \textit{DailyMed Web Services and SPL Resources}. \url{https://dailymed.nlm.nih.gov/dailymed/app-support-web-services.cfm}. Truy cập ngày 24/06/2026.

\bibitem{who_atc}
World Health Organization. \textit{ATC/DDD Toolkit}. \url{https://www.who.int/tools/atc-ddd-toolkit}. Truy cập ngày 24/06/2026.

\bibitem{atc_index}
WHO Collaborating Centre for Drug Statistics Methodology. \textit{ATC/DDD Index 2026}. \url{https://atcddd.fhi.no/atc_ddd_index/}. Truy cập ngày 24/06/2026.

\bibitem{drugbank_interaction}
DrugBank. \textit{Drug-Drug Interaction Checker}. \url{https://go.drugbank.com/clinical/drug_drug_interaction_checker}. Truy cập ngày 24/06/2026.

\bibitem{repo}
SafeRAG Pharma internal implementation and evaluation results. Các kết quả được sử dụng trong báo cáo gồm thống kê corpus, benchmark truy xuất, kiểm thử guardrail, kiểm thử SafeRAG end-to-end và API smoke.

\end{thebibliography}
